---
title: "Similarity"
author: "n9794182"
date: "27 May 2018"
output: html_document
---

### Task3
####display the original dataset
```{r}
mtcars
```
#### Task3.1
####create a function that is used to calculate the distance between the vector and zero
```{r}
getmode<-function(x){
  s<-0
  for (i in c(1:length(x))) {
    s=s+x[i]*x[i]
    
  }
  return(sqrt(s))
}
```
#### create the function that is used to caluculate cosine value between two vectors.
```{r}
cosine<-function(x,y) {
  
  z=getmode(x)*getmode(y)
  return((x%*%y)/z)
}
```

####create a empty matrix A
```{r}
A<-matrix(nrow=32,ncol=32)
```
#### store the cosine value of each pair of vector into the empty matrix A
```{r}

for (i in c(1:32)) {
  for (j in c(1:32)) {
    x<-as.numeric(mtcars[i,])
    y<-as.numeric(mtcars[j,])
    z<-cosine(x,y)
    A[i,j]<-z
  }
  
}
```
####outpu the matrix A
```{r}
print(A)
```
#### Task3.2
```{r}
mtcars

```
####show the name of each vector
```{r}
rownames(mtcars[1,])
```
####find the most value in all the cosine values of each pair of vector and store the pair of vector into matrix Mostsimilarity 
```{r}
Mostsimilarity<-matrix(nrow=32,ncol=2)
leastsimilarity<-matrix(nrow=32,ncol=2)
for (i in c(1:32)) {
  max<-0
  maxi<-0
  maxj<-0
  
  
  for(j in c(1:32)){
    if(i!=j){
      if(A[i,j]>max){
        max<-A[i,j]
        maxi<-i
        maxj<-j
      }
      
    }
  }
  Mostsimilarity[i,1]<-rownames(mtcars[maxi,])
  Mostsimilarity[i,2]<-rownames(mtcars[maxj,])
  
}
Mostsimilarity
```